The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2014-01-22 papers/pair-correlation/paper.tex
Tweaks to the dadz plots for pair-correlation. Tested on paho-arch. Took 0:30.27.

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-1.pdf}\\
  \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-3.pdf}
  \caption{ \paircaption{0.1} \fixme{Fix *ALL* plots to specify units of distance $x/R$.}
  }\label{fig:pair-distribution-1}
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Put all triplets together here.  Tweak spacing, add a, b, c, etc.} The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when
    $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding
    to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path
    shown as a dotted line on the plot to the
    left.}\label{fig:triplet-contact-distribution-3}
\end{figure*}
% \begin{figure}
%   \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-contact-4.pdf}
%   \caption{The triplet distribution function
%     $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.4, plotted when
%     $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
%     shows the triplet distribution function, with white corresponding
%     to the contact value of the \emph{pair} distribution function.
%     The plot on the right shows the value of $g^{(3)}$ along the path
%     shown as a dotted line on the plot to the
%     left.}\label{fig:triplet-contact-distribution-4}
% \end{figure}

@@

\begin{figure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-3-2.pdf}
    \vspace{-0.8cm}
    \caption{Sticky hard-sphere fluid}\label{fig:dadz-delta}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-square-well-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core square well fluid}\label{fig:dadz-square-well}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-inverse-sixth-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core inverse-sixth fluid}\label{fig:dadz-inverse-sixth}
  \end{subfigure}
  \caption{Plot of $\frac{da_1}{dz}$ near a hard
    wall.}\label{fig:dadz}
\end{figure}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-1.pdf}\\
  \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-3.pdf}
  \caption{ \paircaption{0.1} \fixme{Do we want to label the y-axis for the 1d plots?}
  }\label{fig:pair-distribution-1}
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Tweak spacing, add a, b, c, etc. The 1d plots still have two curves for this work, do we want to remove one?} The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when
    $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding
    to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path
    shown as a dotted line on the plot to the
    left.}\label{fig:triplet-contact-distribution-3}
\end{figure*}
% \begin{figure}
%   \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-contact-4.pdf}
%   \caption{The triplet distribution function
%     $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.4, plotted when
%     $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
%     shows the triplet distribution function, with white corresponding
%     to the contact value of the \emph{pair} distribution function.
%     The plot on the right shows the value of $g^{(3)}$ along the path
%     shown as a dotted line on the plot to the
%     left.}\label{fig:triplet-contact-distribution-4}
% \end{figure}

@@

\begin{figure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-3-2.pdf}
    \vspace{-0.8cm}
    \caption{Sticky hard-sphere fluid}\label{fig:dadz-delta}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-square-well-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core square well fluid}\label{fig:dadz-square-well}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-inverse-sixth-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core inverse-sixth fluid}\label{fig:dadz-inverse-sixth}
  \end{subfigure}
  \caption{Plot of $\frac{da_1}{dz}$ near a hard
    wall.\fixme{Do we want y-axis ticks or no? Also, why does the data start
      at $z = 0$?}}
  \label{fig:dadz}
\end{figure}
